### 2014-04-16 inst/vign/taxize_vignette.Rmd
added callopts param to tnrs function

```{r loadtaxize, messages=FALSE, warning=FALSE}
library(taxize)
```

@@

```{r synonyms, eval=TRUE, cache=FALSE, message=FALSE, warning=FALSE, comment=NA}
mynames <- c("Helianthus annuus ssp. jaegeri", "Helianthus annuus ssp. lenticularis", "Helianthus annuus ssp. texanus")
tsn <- get_tsn(mynames)
library(plyr)
ldply(tsn, itis_acceptname)
```

@@

```{r tax_match, cache=FALSE, tidy=FALSE}
A <- "gammarus roeseli"

@@

B1[match(A, B1)]
A_clas[[1]]$Rank[tolower(A_clas[[1]]$ScientificName) %in% B2]
A_clas[[1]]$Rank[tolower(A_clas[[1]]$ScientificName) %in% B3]
```

>>>>

```{r loadtaxize, messages=FALSE, warning=FALSE}
library("taxize")
```

@@

```{r synonyms, eval=TRUE, cache=FALSE, message=FALSE, warning=FALSE, comment=NA}
mynames <- c("Helianthus annuus ssp. jaegeri", "Helianthus annuus ssp. lenticularis", "Helianthus annuus ssp. texanus")
(tsn <- get_tsn(mynames))
library("plyr")
ldply(tsn, itis_acceptname)
```

@@

```{r tax_match, cache=FALSE, tidy=FALSE, message=FALSE}
A <- "gammarus roeseli"

@@

B1[match(A, B1)]
A_clas[[1]]$rank[tolower(A_clas[[1]]$name) %in% B2]
A_clas[[1]]$rank[tolower(A_clas[[1]]$name) %in% B3]
```
